Paper 1 Notebook

### 2023-12-05 minos/outcomes/paper_1_notebook.Rmd
final push with nice mice object

```{r "preamble"}
source("minos/transitions/utils.R")
source("minos/transitions/transition_model_functions.R")
source("minos/transitions/paper_1_plots.R")
library(dplyr)
library(texreg)
library(lme4)
library(glmnet)
library(mice)
library(sjPlot)
library(visreg)
library(ggplot2)
library(ggpattern)
library(VIM)
library(caret)
library(tidyverse)
library(performance)
library(broom.mixed)
library(ggridges)
save.path <- "minos/outcomes/paper1_plots/"
raw.data.dir <- "data/raw_US/"
mice.data.dir <- "data/composite_US/"
final.data.dir <- mice.data.dir
```

@@

# baseline OLS model formula. 
raw_model_formula_string <- "SF_12 ~ factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(labour_state_raw) + 
                  relevel(factor(job_sec), ref=1) +
                  relevel(factor(region), ref='London') +
                  scale(hh_netinc)"

@@

# get only needed variables and replace missing codes with NA.
raw.data <- raw.data[, append(variables, c("time", 'pidp', 'weight'))]
raw.data <- replace.missing(raw.data)

@@

# get raw data file names.
full.raw.filelist <- list.files(raw.data.dir,
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = '[0-9]{4}_US_cohort.csv')[21:30] # get files for 2011-2013.
# load raw data.
full.raw.data <- do.call(rbind, lapply(full.raw.filelist, read.csv))

# get only needed variables and replace missing codes with NA.
full.raw.data <- full.raw.data[, append(variables, c("time", 'pidp', 'weight'))]
full.raw.data <- replace.missing(full.raw.data)
```

@@

squareRootRes <- sqrt(abs(scale(resid(sf12.lm))))
fitted_residuals <- as.data.frame(cbind(fitted(sf12.lm), squareRootRes))
colnames(fitted_residuals) <- c("fitted", "sqrt_residuals")
fitted_residual_plot(fitted_residuals, paste0(save.path, "presentation_fitted_residual_plot.pdf"))

@@

# missingness MICE model formula
mice_formula_string <- "SF_12 ~ 
                        factor(sex) + 
                        relevel(factor(ethnicity), ref='WBI') + 
                        scale(age) + 
                        factor(education_state) + 
                        factor(S7_labour_state) + 
                        relevel(factor(job_sec), ref=1) +
                        relevel(factor(region), ref='London') +
                        scale(hh_income) + 
                        scale(I(hh_income**2)) +
                        factor(housing_quality) +
                        factor(neighbourhood_safety) + 
                        factor(loneliness) +
                        ncigs +
                        nutrition_quality"

@@

imp_columns <- c("SF_12",
                 'sex',
                 "job_sec",
                 "education_state",
                 "S7_labour_state", 
                 "region", 
                 "ethnicity", 
                 "age", 
                 "time", 
                 "hh_income",
                 "housing_quality",
                 "neighbourhood_safety",
                 "loneliness",
                 "ncigs",
                 'nutrition_quality'
)

@@

aggr_columns <- c("SF_12",
                 "job_sec",
                 "education_state",
                 "S7_labour_state", 
                 "ethnicity", 
                 "hh_income",
                 "neighbourhood_safety",
                 "loneliness",
                 "ncigs",
                 'nutrition_quality'
)
# initial missingness structure for 2011-2013 US data.
pdf(paste0(save.path, "total_missingness_structure1.pdf"))
aggr(mice.data[,aggr_columns], sortVars=T, prop=T, combined=F,varheight=T, oma=c(10,5,0,2), gap=0)
dev.off()

mice_columns <- c("age", 
                  "region", 
                  #"heating", 
                  "job_sec", 
                  "ncigs",
                  "education_state",            
                  "ethnicity",
                  "loneliness",
                  "sex", 
                  "SF_12",
                  #"SF_12p",
                  #"smoker",
                  "nkids",       
                  "behind_on_bills",
                  "financial_situation",
                  "future_financial_situation",
                  "likely_move",
                  "ghq_depression",
                  "ghq_happiness",
                  "clinical_depression", 
                  "scsf1",
                  "health_limits_social",
                  #"hhsize",
                  #"housing_tenure",
                  #"urban", 
                  "housing_quality",
                  "hh_income",
                  "neighbourhood_safety",
                  "S7_labour_state",
                  #"yearly_energy",
                  "nutrition_quality"
                  #"hh_comp", 
                  #"marital_status"
)

@@

load_cache <- F
if (load_cache) {
  mice_set <- readRDS("data/transitions/MICE_set.rds")
} else {
  n_iter <- 30
  max_iter <- 10
  ignore_cols = c("birth_year")
  # future mice is parallelised version of MICE.
  mice_set <- mice(data = mice.data[, imp_columns], #method=method,
                   m = n_iter, maxit = max_iter,
                   remove.collinear=T)

@@

mice.long$pidp <- mice.data$pidp
mice.long$weight <- mice.data$weight
mice.long$time <- mice.data$time
mice_set.full <- as.mids(mice.long)

@@

# convergence plots needs to be done on full mice subset. 
pdf(paste0(paste0(save.path,"ols_mice_convergence.pdf")))
print(plot(mice_set, SF_12 = SF_12 ~ .it | .ms))
dev.off()

@@

handover_boxplots(crossval.mice.data, handover.data, "SF_12", save.path, "mice_SF12_boxplots")
density_ridges(crossval.mice.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_raw_ridges")
density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_handover_ridges")

@@

handover_boxplots(crossval.mice.data, handover.data, "SF_12", save.path, "crossval_SF12_boxplot")
density_ridges(crossval.mice.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_raw_ridges")
density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_handover_ridges")

@@

print(coef(cv.lasso, s = "lambda.min"))
print(coef(cv.lasso, s = "lambda.1se"))

# bind two sets of coefficients into a data frame
# load them into a tex table using the latex package?
lasso_coefs <- cbind(coef(cv.lasso, s = "lambda.min")[, 's1'], coef(cv.lasso, s = "lambda.1se")[, 's1'])
colnames(lasso_coefs) <- c("Minimum Error", "First Standard Error")
#lasso_coefs <- kable(as.data.frame(as.matrix(lasso_coefs)), "latex")

texreg_file <- paste0(save.path, 'SF12_Lasso_coefficients.txt')
tex_label <- paste0("table: sf12_lasso_coefficients") 
tex_headers <- c(texreg::names2latex("SF_12 LASSO"))
tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "lasso"))    
lassoTexReg <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,1], se=lasso_coefs[,2])
#lassoTexReg2 <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,2])#, lasso_coefs[, 2]))#, pvalues=lasso_coefs[,2])
#matrixLassoTexReg <- matrixreg(list(lassoTexReg, lassoTexReg2))

@@

iextrapolated.weights.data <- do.call(rbind, lapply(extrapolated_weights.filelist, read.csv))
extrapolated.weights.data <- replace.missing(extrapolated.weights.data)
extrapolated.weights <- extrapolated.weights.data[, c("plus_5_weight")]

@@

# yoink transition model function pre processing
reflect <- T
yeo_johnson <- T
include_weights <- T
depend <- "SF_12"
dependent_data <- complete(mice_set.subset)$SF_12

@@

if (reflect) {
    max_value <- nanmax(mice.data[[depend]])
    glmm.mice.long.subset[, c(depend)] <- max_value - glmm.mice.long.subset[, c(depend)] 
  }
if (yeo_johnson)
{
  yj <- yeojohnson(glmm.mice.long.subset[["SF_12"]])
  glmm.mice.long.subset[["SF_12"]] <- predict(yj)
}

min_value <- nanmin(glmm.mice.long.subset [[depend]])
glmm.mice.long.subset[[depend]] <- glmm.mice.long.subset[[depend]] - min_value + 0.001

@@

glmm_model_formula_string <- "SF_12 ~ SF_12_last +
                  factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(S7_labour_state) + 
                  relevel(factor(job_sec), ref=1) +
                  relevel(factor(region), ref='London') +
                  scale(hh_income) + 
                  scale(I(hh_income**2)) +
                  factor(housing_quality) +
                  factor(neighbourhood_safety) +
                  factor(loneliness) + 
                  nutrition_quality + 
                  ncigs + 
                  (1|pidp)"

sf12.glmm.model <- with(glmm.mice.set, glmer(glmm_model_formula_string,  
               nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes forever..
               family=Gamma(link='log'), # gamma family with log link.
               weights=weight))

@@

# + rnorm(nrow(complete(glmm.mice.set ,1)), 0,0.75)
glmm.fitted <- (max_value - predict(yj, predict(mice.glmm.object, type='response') + min_value +rnorm(predict(mice.glmm.object, type='response'),0,0.2), inverse=T))#
#glmm.fitted <- (max_value - predict(mice.glmm.object, type='response') + min_value + rnorm(nrow(glmm.mice.long.subset), 0, 1))
glmm.fitted <- trunc(glmm.fitted, 0 , 100)
qq_plot(residuals(mice.glmm.object, type='pearson'), paste0(save.path, "glmm_qq.pdf"))
residual_density_plot(res=residuals(mice.glmm.object) , file_name=paste0(save.path, "glmm_residual_density.pdf"), guide="normal")

squareRootRes <- sqrt(residuals(mice.glmm.object, type='pearson'))
fitted_residuals <- as.data.frame(cbind(glmm.fitted, squareRootRes))
colnames(fitted_residuals) <- c("fitted", "sqrt_residuals")
fitted_residual_plot(fitted_residuals, paste0(save.path, "glmm_fitted_residual_plot.pdf"))

@@

rolling.data <- start.data
for (i in 1:7){
  rolling.data$SF_12 <- max_value - predict(yj,  predict(mice.glmm.object, start.data, type='response',allow.new.levels=T) + rnorm(nrow(rolling.data),0,0.25)+min_value, inverse=T)
  #rolling.data$SF_12 <- max_value - rolling.data$SF_12
  rolling.data$SF_12 <- trunc(rolling.data$SF_12, 0 , 100)
  rolling.data$SF_12_last <- rolling.data$SF_12
  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
  handover.data <- rbind(handover.data, rolling.data)
}

>>>>

```{r "preamble"}
source("minos/transitions/utils.R")
source("minos/transitions/transition_model_functions.R")
source("minos/transitions/paper_1_plots.R")
library(dplyr)
library(texreg)
library(lme4)
library(glmnet)
library(mice)
library(sjPlot)
library(visreg)
library(ggplot2)
library(ggpattern)
library(VIM)
library(caret)
library(tidyverse)
library(performance)
library(broom.mixed)
library(ggridges)
library(ggmice)
library(MASS)
save.path <- "minos/outcomes/paper1_plots/"
raw.data.dir <- "data/raw_US/"
mice.data.dir <- "data/composite_US/"
final.data.dir <- mice.data.dir
```

@@

# baseline OLS model formula. 
raw_model_formula_string <- "SF_12 ~ factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(labour_state_raw) + 
                  relevel(factor(NSSEC), ref=1) +
                  relevel(factor(region), ref='London') +
                  scale(hh_netinc)"

@@

# get only needed variables and replace missing codes with NA.
raw.data.colnames <- colnames(raw.data)
raw.data.colnames[which( colnames(raw.data)=="job_sec" )] <- "NSSEC"
colnames(raw.data) <- raw.data.colnames
raw.data <- raw.data[, append(variables, c("time", 'pidp', 'weight'))]
raw.data <- replace.missing(raw.data)

@@

# get raw data file names.
full.raw.filelist <- list.files(raw.data.dir,
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = '[0-9]{4}_US_cohort.csv')[21:30] # get files for 2011-2013.
# load raw data.
full.raw.data <- do.call(rbind, lapply(full.raw.filelist, read.csv))
full.raw.data.colnames <- colnames(full.raw.data)
full.raw.data.colnames[which( colnames(full.raw.data)=="job_sec" )] <- "NSSEC"
colnames(full.raw.data) <- full.raw.data.colnames
# get only needed variables and replace missing codes with NA.
full.raw.data <- full.raw.data[, append(variables, c("time", 'pidp', 'weight'))]
full.raw.data <- replace.missing(full.raw.data)
```

@@

squareRootRes <- sqrt(abs(scale(resid(sf12.lm))))
fitted_residuals <- as.data.frame(cbind(fitted(sf12.lm), squareRootRes))
colnames(fitted_residuals) <- c("fitted", "sqrt_residuals")
fitted_residual_plot(fitted_residuals, paste0(save.path, "presentation_scale_location_plot.pdf"))

@@

mice.data.colnames <- colnames(mice.data)
mice.data.colnames[which(colnames(mice.data)=="job_sec" )] <- "NSSEC"
colnames(mice.data) <- mice.data.colnames

# missingness MICE model formula
mice_formula_string <- "SF_12 ~ 
                        factor(sex) + 
                        relevel(factor(ethnicity), ref='WBI') + 
                        scale(age) + 
                        factor(education_state) + 
                        factor(S7_labour_state) + 
                        relevel(factor(NSSEC), ref=1) +
                        relevel(factor(region), ref='London') +
                        scale(hh_income) + 
                        scale(I(hh_income**2)) +
                        factor(housing_quality) +
                        factor(neighbourhood_safety) + 
                        factor(loneliness) +
                        ncigs +
                        nutrition_quality"

@@

imp_columns <- c("SF_12",
                 'sex',
                 "NSSEC",
                 "education_state",
                 "S7_labour_state", 
                 "region", 
                 "ethnicity", 
                 "age", 
                 "time", 
                 "hh_income",
                 "housing_quality",
                 "neighbourhood_safety",
                 "loneliness",
                 "ncigs",
                 'nutrition_quality'
)

@@

aggr_columns <- c("SF_12",
                 "NSSEC",
                 "education_state",
                 "S7_labour_state", 
                 "ethnicity", 
                 "hh_income",
                 "neighbourhood_safety",
                 "loneliness",
                 "ncigs",
                 'nutrition_quality'
)
# initial missingness structure for 2011-2013 US data.
pdf(paste0(save.path, "total_missingness_structure1.pdf"))
aggr(mice.data[,aggr_columns], sortVars=T, prop=T, combined=F,varheight=T, oma=c(10,5,1,2), gap=0)
dev.off()

mice_columns <- c("age", 
                  "region", 
                  #"heating", 
                  "NSSEC", 
                  "ncigs",
                  "education_state",            
                  "ethnicity",
                  "loneliness",
                  "sex", 
                  "SF_12",
                  #"SF_12p",
                  #"smoker",
                  "nkids",       
                  "behind_on_bills",
                  "financial_situation",
                  "future_financial_situation",
                  "likely_move",
                  "ghq_depression",
                  "ghq_happiness",
                  "clinical_depression", 
                  "scsf1",
                  "health_limits_social",
                  #"hhsize",
                  #"housing_tenure",
                  #"urban", 
                  "housing_quality",
                  "hh_income",
                  "neighbourhood_safety",
                  "S7_labour_state",
                  #"yearly_energy",
                  "nutrition_quality"
                  #"hh_comp", 
                  #"marital_status"
)

@@

load_cache <- T
if (load_cache) {
  mice_set <- readRDS("data/transitions/MICE_set.rds")
} else {
  n_iter <- 30
  max_iter <- 10
  ignore_cols = c("birth_year")
  # future mice is parallelised version of MICE.
  mice_set <- mice(data = mice.data[, imp_columns],
                   m = n_iter, maxit = max_iter,
                   remove.collinear=T)

@@

mice.long$pidp <- mice.data$pidp
mice.long$weight <- mice.data$weight
mice.long$time <- mice.data$time
mice.long.colnames <- colnames(mice.long)
mice.long.colnames[which( colnames(mice.long)=="job_sec" )] <- "NSSEC"
colnames(mice.long) <- mice.long.colnames

mice_set.full <- as.mids(mice.long)

@@

# convergence plots needs to be done on full mice subset. 
pdf(paste0(paste0(save.path,"ols_mice_convergence.pdf")))
#print(plot(mice_set, SF_12 = SF_12 ~ .it | .ms))
plot_trace(mice_set, "SF_12") + theme(legend.position="none")
dev.off()

@@

handover_boxplots(crossval.mice.data, handover.data, "SF_12", save.path, "mice_SF12_boxplots")
density_ridges(crossval.mice.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_raw_ridges")
density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "mice_validation_ridges")

@@

handover_boxplots(crossval.mice.data, handover.data, "SF_12", save.path, "crossval_SF12_boxplot")
density_ridges(crossval.mice.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_raw_ridges")
density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "crossval_validation_ridges")

###

```{r random_coefficients}

# for 100 iterations
randomised.mice.model.data <- data.frame()
random.mice.lm.object <- lm(mice_formula_string, data = complete(mice_set.subset, 1))

for (i in 1:100) {
  # choose a random OLS model
  # randomise its coefficients from MVN dist from MASS.
  #model.choice.ix <- ceiling(runif(1)*30)
  #model.choice <- mice.sf12.lm$analyses[model.choice.ix]
  model.choice <- random.mice.lm.object
  model.choice$coefficients <- MASS::mvrnorm(n=1, mu=mice.lm.object$coefficients[, 1], Sigma=vcov(mice.lm.object))
  # add to pool
  # commentary
  random.start.data <- crossval.mice.data[which(crossval.mice.data$time==2013),]
  #random.start.data[, c("run_id")] <- i
  #random.rolling.data <- random.start.data[, c("SF_12", "time", "run_id")]
  #random.handover.data <- rolling.data
  for (j in 1:7){
    random.start.data$SF_12 <- predict(model.choice, random.start.data)
    #random.start.data$SF_12 <- random.rolling.data$SF_12
    #random.rolling.data[, 'time'] <- random.rolling.data[, 'time'] +1
    #random.handover.data <- rbind(random.handover.data, random.rolling.data)
  }
  individual.density <- density(random.start.data$SF_12)
  new.data.frame <- cbind(individual.density$x, individual.density$y, i)
  colnames(new.data.frame) <- c("SF_12", "Density", "run_id")
  randomised.mice.model.data <- rbind(randomised.mice.model.data, new.data.frame)

}

p <- ggplot(randomised.mice.model.data, aes(x=SF_12, y=Density, group=factor(run_id))) +
     geom_line(alpha=0.1) + ylim(0, 0.15) + xlim(15,60)
ggsave(paste0(save.path, "/", "randomised_coefficients_2020_density.pdf"))
#ggplot(randomised.mice.model.data, aes(x=SF_12, y=Density)) +
#    geom_line(alpha=0.2) + geom_ribbon()

@@

# bind two sets of coefficients into a data frame
# load them into a tex table using the latex package?
lasso.min.coefs <- coef(cv.lasso, s=cv.lasso$lambda.min)
lasso.1se.coefs <- coef(cv.lasso, s=cv.lasso$lambda.1se)
lasso_model_names <- c("Minimum Error", "First Standard Error")

texreg_file <- paste0(save.path, 'SF12_Lasso_coefficients.txt')
tex_label <- paste0("table: sf12_lasso_coefficients") 
tex_headers <- c(texreg::names2latex("Minimum Error"), texreg::names2latex("First Standard Error"))
tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "lasso"))    
#lassoTexReg <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,1], se=lasso_coefs[,2], model.names=c("Minimum Error", "First Standard Error"))

lasso.min <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso.min.coefs[, "s1"])
lasso.1se <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso.1se.coefs[, "s1"])

#lassoTexReg2 <-createTexreg(coef.names=rownames(lasso_coefs), coef = lasso_coefs[,2])#, lasso_coefs[, 2]))#, pvalues=lasso_coefs[,2])
#matrixLassoTexReg <- matrixreg(list(lassoTexReg, lassoTexReg2))

texreg(c(lasso.min, lasso.1se), # what model to save coefs for. 
       file=texreg_file,  # where to save.
       custom.model.names = tex_headers, # title of table.
       caption=tex_caption, # \caption command option. 
       label = tex_label, # \label command option. 
       dcolumn=T,# nice column alignment. 
       booktabs=T, # nice hlines. (recommended)
       tabular=T,# tabulr env.
       single.row = T, # nicer one row formatting.
       longtable=T, # allows tables to wrap over pages
       use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
       fontsize='small') # small font

@@

extrapolated.weights.data <- do.call(rbind, lapply(extrapolated_weights.filelist, read.csv))
extrapolated.weights.data <- replace.missing(extrapolated.weights.data)
extrapolated.weights <- extrapolated.weights.data[, c("plus_5_weight")]

@@

# yoink transition model function pre processing
reflect <- T
yeo_johnson <- F
include_weights <- T
depend <- "SF_12"
dependent_data <- complete(mice_set.subset)$SF_12

@@

if (reflect) {
    max_value <- nanmax(mice.data[[depend]])
    glmm.mice.long.subset[, c(depend)] <- max_value - glmm.mice.long.subset[, c(depend)] + 0.001
  }
if (yeo_johnson)
{
  yj <- yeojohnson(glmm.mice.long.subset[["SF_12"]])
  glmm.mice.long.subset[["SF_12"]] <- predict(yj)

  min_value <- nanmin(glmm.mice.long.subset [[depend]])
  glmm.mice.long.subset[[depend]] <- glmm.mice.long.subset[[depend]] - min_value + 0.001
}

@@

asd <- "SF_12_last +"
glmm_model_formula_string <- "SF_12 ~ SF_12_last +
                  factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(S7_labour_state) + 
                  relevel(factor(NSSEC), ref=1) +
                  relevel(factor(region), ref='London') +
                  scale(hh_income) + 
                  scale(I(hh_income**2)) +
                  factor(housing_quality) +
                  factor(neighbourhood_safety) +
                  factor(loneliness) + 
                  nutrition_quality + 
                  ncigs + time +
                  (1|pidp)"

sf12.glmm.model <- with(glmm.mice.set, glmer(glmm_model_formula_string,  
               nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes forever..
               family=Gamma(link='log')#, weights=weight# gamma family with log link.
               ))

@@

# + rnorm(nrow(complete(glmm.mice.set ,1)), 0,0.75)
if (yeo_johnson == T) {
  glmm.fitted <- (max_value - predict(yj, predict(mice.glmm.object, type='response') + min_value #+rnorm(predict(mice.glmm.object, type='response'),0,0.2)
                                    , inverse=T))#
} else {
  glmm.fitted <-  max_value - predict(mice.glmm.object, type='response')
}

#glmm.fitted <- (max_value - predict(mice.glmm.object, type='response') + min_value + rnorm(nrow(glmm.mice.long.subset), 0, 1))
#glmm.mean <- mean(glmm.fitted)
#glmm.sd <- sd(glmm.fitted)
#glmm.fitted <- glmm.fitted * (glmm.sd/sd(raw.data$SF_12))
#glmm.fitted <- glmm.fitted - (glmm.mean*(glmm.sd/sd(raw.data$SF_12)-1))
#glmm.fitted <- trunc(glmm.fitted, 0 , 100) #+ rnorm(length(glmm.fitted),0,2)

qq_plot(scale(residuals(mice.glmm.object, type='pearson')), paste0(save.path, "glmm_qq.pdf"))
qq_plot(scale(residuals(mice.glmm.object, type='deviance')), paste0(save.path, "glmm_qq.pdf"))

residual_density_plot(res=residuals(mice.glmm.object) , file_name=paste0(save.path, "glmm_residual_density.pdf"), guide="normal")

squareRootRes <- sqrt(residuals(mice.glmm.object, type='pearson')**2)
#squareRootRes <- residuals(mice.glmm.object, type='pearson')

fitted_residuals <- as.data.frame(cbind(glmm.fitted, squareRootRes))
colnames(fitted_residuals) <- c("fitted", "sqrt_residuals")
fitted_residual_plot(fitted_residuals, paste0(save.path, "glmm_scale_location_plot.pdf"))

@@

rolling.data <- start.data
for (i in 1:7){
  if (yeo_johnson) {
      rolling.data$SF_12 <- max_value - predict(yj,  predict(mice.glmm.object, start.data, type='response',allow.new.levels=T) +min_value, inverse=T)
  }
  else {
    rolling.data$SF_12 <- max_value - predict(mice.glmm.object, start.data,type='response',allow.new.levels=T) + rnorm(nrow(rolling.data), 0, 1)
  }
  #rolling.data$SF_12 <- max_value - rolling.data$SF_12
  rolling.data$SF_12 <- trunc(rolling.data$SF_12, 0 , 100)
  rolling.data$SF_12_last <- rolling.data$SF_12
  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
  handover.data <- rbind(handover.data, rolling.data)
}
